A re-examination of the role of friction in the original Social Force Model

### 2019-06-16 paper.tex
emprolije el parrafo donde introducimos los parametros de la ecuacion de unidades reducidas

\textcolor{red}{Our starting point is the re-examination of the (basic) SFM. 
We propose a reduce-in-units equation of motion of the SFM. The social 
force $\mathbf{f}_s$ depends on an intensity $\mathcal{A}$ while the granular force $\mathbf{f}_g$ depends
on $\mathcal{K}$. In Section~\ref{appendix_1} we derivate this reduce-in-units equation of motion
and its corresponding control parameters. }\\

%Our starting point is the re-examination of the (basic) SFM.
%\textcolor{red}{We propose a reduce-in-units equation of motion of 
%the SFM (Eq.~\ref{eqn_appendix_1} and Eq.~\ref{eqn_appendix_2}). This leads us
%to two control parameters} $\mathcal{A}$ and $\mathcal{K}$ (see Section~\ref{appendix_1}) that may handle
%the collective motion in dense crowds.

>>>>

\textcolor{red}{Our starting point is the re-examination of the (basic) SFM. 
We propose a reduce-in-units equation of motion of the SFM. In this new picture,
the social force $\mathbf{f}_s$ depends on an intensity $\mathcal{A}$, the granular
force $\mathbf{f}_g$ depends on $\mathcal{K}$, and the desired force $\mathbf{f}_d$
only depends on the target. In Section~\ref{appendix_1} we derivate this 
reduce-in-units equation of motion and its corresponding control parameters ($\mathcal{A}$ and $\mathcal{K}$). }\\
